---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# omopViewer

<!-- badges: start -->
[![R-CMD-check](https://github.com/oxford-pharmacoepi/omopViewer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/oxford-pharmacoepi/omopViewer/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/omopViewer)](https://CRAN.R-project.org/package=omopViewer)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/oxford-pharmacoepi/omopViewer/branch/main/graph/badge.svg)](https://app.codecov.io/gh/oxford-pharmacoepi/omopViewer?branch=main)
<!-- badges: end -->

> [!IMPORTANT]
> This package is under construction and this is just a first Beta release, please use it carefully and report any issue that you encounter using it.

The goal of omopViewer is to allow the user to easily create Shiny Apps to visualise study results in `<summarised_result>` format.

## Installation

You can install the development version of omopViewer from [GitHub](https://github.com/oxford-pharmacoepi/omopViewer) with:

``` {r, eval = FALSE}
install.packages("pak")
pak::pkg_install("oxford-pharmacoepi/omopViewer")
```

## Main functionalities

```{r}
library(omopViewer)
```

The package can be divided in 3 main functionalities:
- Static shiny app
- Dynamic shiny app
- Utility functions

## Static shiny app

The static shiny app functionality creates a static shiny from a list of `summarised_result` objects. This shiny is specific to the set of results and can be modified later locally.

```{r, message=TRUE}
# lets generate some results
library(CohortCharacteristics)
cdm <- mockCohortCharacteristics()
result <- summariseCharacteristics(cdm$cohort1) |>
  bind(summariseCohortAttrition(cdm$cohort1))

exportStaticApp(result = result)
```

## Dynamic shiny app

The dynamic shiny app can be easily launched with `launchDynamicApp()` function. This function creates a shinyApp where you can upload multiple results sets and visualise them.

```{r, eval = FALSE}
launchDynamicApp()
```

## Utility functions

- `tidyData` is an experimental version of the `tidy.summarised_result` method defined in **visOmopResults**.
- `omopViewerTable` is an experimental version of the `visOmopTable` function defined in **visOmopResults**.
- `filterData` is a function used internally in the package to subset the result. It is not meant to be for user use. It is exported because it is used in the *exportStaticApp()* function.
