---
title: "Edit the background panel of your shiny using `background.md`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{background}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The background panel is triggered when `background = TRUE` argument is used in the `exportStaticApp()` function. If background is set to TRUE a 'background' panel is added and a default 'background.md' file is created. The content of this 'background' will be always a card generated with the `cardFromMd()` function using the content of 'background.md'. In this vignette we are going to show different options how to populate the 'background.md'.

```{r}
library(omopViewer)
```

## `bslib::card()` arguments

We can control the arguments of the `bslib::card()` using the

## Keywords

The following keywords can be used to edit the `bslib::card()` content:

```{r, echo=FALSE}
omopViewer:::backgroundKeywords |>
  dplyr::mutate(`function` = purrr::map2(.data$link, .data$fun, \(x, y) {
    shiny::a(href = x, y) |>
      as.character() |>
      gt::html()
  })) |>
  dplyr::select(!c("fun", "link")) |>
  gt::gt()
```
