---
title: "How to Delete Tabs/Panels Using `panelDetails`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{configured_panels}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=FALSE}
library(OmopViewer)
```

### Generating a Static Shiny App

In this example, we will first ll create a static Shiny app using a filtered subset of result types:
```{r}
result <- omopViewerResults |>
  omopgenerics::filterSettings(
    result_type %in% c("summarise_omop_snapshot", "summarise_characteristics", "prevalence")
  )
```

### Removing a Specific Panel Within a Tab

To remove the `tidy` panel under the `summarise_omop_snapshot` tab:
```{r}
panelDetails = panelDetailsFromResult(result)
panelDetails$summarise_omop_snapshot$content$tidy <- NULL
exportStaticApp(result = result, directory = tempdir(),
                panelDetails = panelDetails)
```

### Removing an Entire Tab

To remove the entire `summarise_omop_snapshot` tab:
```{r}
panelDetails = panelDetailsFromResult(result)
panelDetails$summarise_omop_snapshot <- NULL
exportStaticApp(result = result, directory = tempdir(),
                panelDetails = panelDetails)
```
This approach allows you to customise which panels or entire tabs are included in the generated static app.
