---
title: "Dynamic app"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dynamic_app}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This vignette shows how to visualise results dynamically in *Shiny apps* using the `OmopViewer` package. These dynamic shiny apps allow very little customisation and are not deployable or editable, if you seek a more flexible approach please see the [Static app](export_static_app.Rmd) vignette.

## Dynamic app

```{r setup}
library(OmopViewer)
```

To launch the dynamic app please use the following command:

```{r, eval=FALSE}
launchDynamicApp()
```

Use the **Upload data** to upload a csv result exported using `exportSummarisedResult()` and then click the button **Bind data and load shiny** to create panels for the uploaded data. One panel will be created per summarised result. You can easily navigate thought the different tabs to see whats on your data.
