---
title: "Create a static shiny app"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{export_static_app}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette demonstrates the creation of Shiny apps using the `OmopViewer` package. We'll use the `omopViewerResults` mock data  from this pacakge for illustration. 
### Loading Necessary Libraries and Data
First, load the required library and see the structure of the sample data:
```{r}
library(OmopViewer)
# Inspect the structure of the sample data
summary(omopViewerResults)
```

### Subsetting the Data
For this example, we'll use a subset of the data containing specific result types:
```{r}
result <- omopViewerResults |>
  omopgenerics::filterSettings(
    result_type %in% c("summarise_omop_snapshot", "summarise_characteristics", "incidence")
  )
```
This filters the `omopViewerResults` data to include only entries where result_type is one of "summarise_omop_snapshot", "summarise_characteristics", or "incidence". 

### Generating the Shiny App

The exportStaticApp function generates a Shiny app from the prepared data. Using the default parameters, it only requires a directory to save the app and the processed data (a <summarised_result> object):

```{r}
exportStaticApp(result = result, directory = tempdir())
```

### Panel Structure (omopViewerPanels)

The arrangement of panels within the app is controlled by the `panelStructure` variable. This variable determines how panels are grouped into logical sections or tabs within the Shiny app. By default, `omopViewerPanels` is used to define the panel layout when no specific `panelStructure` is provided to `exportStaticApp.`
```{r}
omopViewerPanels
```
The list shows predefined groups of result_type. Then this can be input into `exportStaticApp` function in `panelStructure` parameter to organise the generated tabs in the Shiny app. Panels whose result_type is found within one of these named groups in the list will be in the same tab.


### Customise panelStructure
```{r}
ps1 <- list(
  grp_1 = c("summarise_omop_snapshot", "incidence"),
  grp_2 = c("summarise_characteristics")
)

exportStaticApp(result = result, directory = tempdir(), panelStructure = ps1)
```
This custom `panelStructure` groups the "summarise_omop_snapshot" and "incidence" result types together in grp_1, while placing the "summarise_characteristics" result type in grp_2. You can pass this custom structure to `exportStaticApp` to organize the panels according to your preference.

### Understanding Panel Details (panelDetails)
Now that we have an overall panel structure, the specific details of the panels to be created are defined by the `panelDetails` argument. By default, a tab is generated for each result_type in the result object. If no specific tab is defined for a given result_type in omopViewerPanels, the default tab (`getPanel("default")`) will be used. Let’s inspect the default `panelDetails`:

```{r}
panelDetails <- panelDetailsFromResult(result)
panelDetails
```
### Breakdown of Panel Details
Each panel’s entry contains key information:

1. Icon: Defines the icon displayed next to the panel, helping to visually distinguish between the different types of panels (e.g., clipboard-list, chart-line ...).

2. Data: The result_type reflects the type of result associated with the panel. This helps to understand which data to use for rendering the current panel.

3. Filters: Filters (filters + automatic_filters) that allow users to refine the results within each panel. Each panel has its own defaults. For example, the default incidence panel includes automatic_filters: "settings", "variable_name" and filters: "cdm_name"


4. Content: Defines the types of content displayed in the panel, such as tables (DT, gt) and plots (ui). For example, the `summarise_omop_snapshot` panel includes a table displaying the snapshot data and a gt table generated from that snapshot data.

All of these elements - icon, data, filters, and content - can be customised by the user if needed.
