---
title: "Create a static shiny app"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{export_static_app}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette we show the basis to create shiny apps. To do so we will use the mock results provided by the package:

```{r}
library(OmopViewer)
omopViewerResults
summary(omopViewerResults)
```

Let's use a subset of the default result data set:

```{r}
result <- omopViewerResults |>
  omopgenerics::filterSettings(
    result_type %in% c("summarise_omop_snapshot", "summarise_characteristics", "incidence")
  )
```


Using the default parameters you only have to provide a directory and a <summarised_result> object.

```{r}
exportStaticApp(result = result, directory = tempdir())
```

The panels that will be created are defined by the `panelDetails` argument. By default, a tab is created by each `result_type` of the result object. The default tab `getPanel("default")` is used if no tab is defined for that `result_type` in **omopViewerPanels**. Let's see the default `panelDetails`:

```{r}
panelDetails <- panelDetailsFromResult(result)
panelDetails
```

