---
title: "Plot tabs in OmopViewer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{supported_result_type}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **OmopViewer** package supports `r OmopViewer:::omopViewerTabs$result_type |> unique() |> length()` different result types of the following packages:

```{r, results='asis', echo=FALSE}
pkgs <- OmopViewer:::omopViewerTabs$package |> unique() |> sort()
for (k in seq_along(pkgs)) {
  cat(paste0("* ", pkgs[k], "\n"))
}
```

You can see the plot functions that have been configured in the package per result type in the following table:

```{r, echo = FALSE}
OmopViewer:::omopViewerPlots |>
  dplyr::inner_join(
    OmopViewer:::omopViewerTabs, by = "result_tab_id"
  ) |>
  dplyr::select(
    "Result type" = "result_type", "package", "Plot function" = "fun") |>
  visOmopResults::gtTable(
    groupColumn = "package", colsToMergeRows = "Result type")
  
```

## Note for developers

There exist a default design for an "unconfigured" `result_type` if you wish to configure a new `result_type` this can be done editing the internal data: *omopViewerTabs*, *omopViewerPlots* and *omopViewerPlotArguments* in file [internalData.R](https://github.com/OHDSI/omopViewer/blob/main/data-raw/internalData.R). Please feel free to submit your PR.

<!-- :::{callout} -->
<!-- ::: -->
