---
title: "Theming your shiny"
output: 
  html_document:
    theme: null
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Theming in `OmopViewer` shiny apps is done using [brand.yml](https://posit-dev.github.io/brand-yml/), that will rely on a `_brand.yml` file written in the root of your shiny project. That `_brand.yml` file customises your shiny app colour and also the tables and plots created using [visOmopresults](https://darwin-eu.github.io/visOmopResults/). The package has some predefined themes, some come from the `visOmopResults` package and some others defined here in `OmopViewer`.

```{r, echo=FALSE}
OmopViewer:::availableThemes() |>
  purrr::map(dplyr::as_tibble) |>
  dplyr::bind_rows(.id = "package") |>
  dplyr::rename("Theme" = "value") |>
  gt::gt(groupname_col = "package") |>
  gt::tab_style(
    style = list(
      gt::cell_text(color = "white", weight = "bold"),
      gt::cell_fill(color = "gray")
    ), 
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_options(column_labels.hidden = TRUE)
```

## Predefined themes

See our predefined themes:

<div style="border: 1px solid #ccc; overflow: hidden;">
  <iframe 
    src="https://dpa-pde-oxford.shinyapps.io/OmopViewerThemes/" 
    style="border: none; width: 100%; height: 300px;">
  </iframe>
</div>
